Moral Foundations of U.S. Political News Organizations

### 2020-07-29 thesis/pilot_manuscript.Rmd
updating

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
replace_ampersands: yes
csl               : apa6.csl
---

@@

```{r appendix_mfd, eval = T, include = T}
orig_mfd = read.csv("exp1_data/original_mfd.csv")
####build the table here####
tableprint = matrix(NA, nrow=length(orig_mfd), ncol=5)
colnames(tableprint) = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity")

#tableprint[ , 1] = unique(final_gs$Source)
tableprint[ , 1] = orig_mfd[,1]
tableprint[ , 2] = orig_mfd[,2]
tableprint[ , 3] = orig_mfd[,3]
tableprint[ , 4] = orig_mfd[,4]
tableprint[ , 5] = orig_mfd[,5]

>>>>

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
replace_ampersands: yes
csl               : apa6.csl
---

@@

```{r appendix_mfd, results = 'asis', echo = FALSE, message = F}
orig_mfd = read.csv("exp1_data/original_mfd.csv", stringsAsFactors = F, fileEncoding="UTF-8")
####build the table here####
tableprint = matrix(NA, nrow=length(orig_mfd), ncol=5)
colnames(tableprint) = c("Harm/Care", "Fairness/Reciprocity", "Ingroup/Loyalty", "Authority/Respect", "Purity/Sanctity")

#tableprint[ , 1] = unique(final_gs$Source)
#tableprint[ , 1] = orig_mfd[,1]
#tableprint[ , 2] = orig_mfd[,2]
#tableprint[ , 3] = orig_mfd[,3]
#tableprint[ , 4] = orig_mfd[,4]
#tableprint[ , 5] = orig_mfd[,5]
